---
title: "ERGM"
author: "Jorge"
date: "3/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages loading

```{r initialize, message= FALSE, warning=FALSE}
library(sand)
library(robustbase)
library(igraph)
library(ggplot2)
library(dplyr)
library(maditr)
library(textshape)
library(VIF)
library(bipartite)
library(sjstats)
library(Hmisc)
library(network)
library(nlme)
library(ergm.count)
library(readr)
library(mvtnorm)
library(ggstance)
library(jtools)
library(tibble)
library(broom.mixed)
library(jtools)
library(patchwork)
require(ergm.count)
```

# Data loading

```{r Data loading, message= FALSE, warning=FALSE}
data <- read_delim ("~/Documents/GitHub/JEcology_Isla2022/data/dataset.csv", ";", escape_double = FALSE, trim_ws = TRUE)
require(tibble)
data<-column_to_rownames(data, var = "tree")%>% 
  mutate(area = factor(area, levels = c("SABCOL", "SABOJI", "SABMAR"))) # tree identification to row names.
sabcolors <- c("SABCOL"="#35978f", "SABOJI"="#dfc27d", "SABMAR"="#8c510a") # color fix
```

# Data to numeric, round, and splitting per stand
```{r Data to numeric, round, and splitting per stand}

#Traits to numeric
data$d1                            <- as.numeric(data$d1) 
data$h                             <- as.numeric(data$h) 
data$collapsed_cropsize            <- as.numeric(data$collapsed_cropsize) 
data$diam                          <- as.numeric(data$diam) 
data$nseed                         <- as.numeric(data$nseed) 
data$oneseedw                      <- as.numeric(data$oneseedw)
data$sunken                        <- as.numeric(data$sunken)

data$neighboiurhood_cropsize       <- as.numeric(data$neighboiurhood_cropsize)
data$n_neigh                       <- as.numeric(data$n_neigh)

data$area                          <- as.factor(data$area)

#Interactions to numeric
data$fa_4cone_chl      <- as.numeric(data$fa_4cone_chl)
data$fa_apo            <- as.numeric(data$fa_apo)
data$fa_mus            <- as.numeric(data$fa_mus)
data$fa_elachista      <- as.numeric(data$fa_elachista)
data$fa_mesophleps     <- as.numeric(data$fa_mesophleps)
data$fa_nanodiscus     <- as.numeric(data$fa_nanodiscus)
data$fa_megastigmus    <- as.numeric(data$fa_megastigmus)


# Splitting per area

dataCOL<-data[c(1:35),]
dataOJI<-data[c(71:105),]
dataMAR<-data[c(36:70),]

#Selecting interactions rows
int<-data %>% 
           dplyr::select(17,18,19,20,21,22,23)
intCOL <- dataCOL %>% 
           dplyr::select(17,18,19,20,21,22,23)
intOJI <- dataOJI %>% 
           dplyr::select(17,18,19,20,21,22,23)
intMAR <- dataMAR %>% 
           dplyr::select(17,18,19,20,21,22,23)

#Round to avoid computation problems
int <- round(int*100, digits = 0)
intCOL <- round(intCOL*100, digits = 0)
intOJI <- round(intOJI*100, digits = 0)
intMAR <- round(intMAR*100, digits = 0)

#Check dimensions, names and plants for stand
#dim(int)
#dim(intCOL)
#dim(intOJI)
#dim(intMAR)
#names(int)
#names(intCOL)
#names(intOJI)
#names(intMAR)
#row.names(int)
#row.names(intCOL)
#row.names(intOJI)
#row.names(intMAR)
```
# Igraph object creation
```{r Igraph object creation}
net.int<- graph_from_incidence_matrix(int, weighted= T, add.names=NULL) 
net.COL<- graph_from_incidence_matrix(intCOL, weighted= T, add.names=NULL) 
net.OJI<- graph_from_incidence_matrix(intOJI, weighted= T, add.names=NULL)
net.MAR<- graph_from_incidence_matrix(intMAR, weighted= T, add.names=NULL) 
class(net.int)
```

# Creation of attribute dataset, scaling, and assigning them to each igraph object
```{r Creation of attribute dataset, scaling, and assigning them to each igraph object, message= FALSE, warning=FALSE}

#traits dataset fix
node.traits <- data %>%  
           dplyr::select(c(1, 2,4,6,7,8,10,12,14,16))
node.traits.COL <- dataCOL %>%  
           dplyr::select(c(1, 2,4,6,7,8,10,12,14,16))
node.traits.OJI <- dataOJI %>%  
           dplyr::select(c(1, 2,4,6,7,8,10,12,14,16))
node.traits.MAR <- dataMAR %>%  
           dplyr::select(c(1, 2,4,6,7,8,10,12,14,16))

#Scaling traits

#Big-picture
node.traits$d1                       <- scale(node.traits$d1)
node.traits$h                        <- scale(node.traits$h)
node.traits$collapsed_cropsize       <- scale(node.traits$collapsed_cropsize)
node.traits$diam                     <- scale(node.traits$diam)
node.traits$nseed                    <- scale(node.traits$nseed)
node.traits$sunken                   <- scale(node.traits$sunken)
node.traits$oneseedw                 <- scale(node.traits$oneseedw)
node.traits$sunken                   <- scale(node.traits$sunken)
node.traits$neighboiurhood_cropsize  <- scale(node.traits$neighboiurhood_cropsize)
node.traits$n_neigh                  <- scale(node.traits$n_neigh)
#COL
node.traits.COL$d1                       <- scale(node.traits.COL$d1)
node.traits.COL$h                        <- scale(node.traits.COL$h)
node.traits.COL$collapsed_cropsize       <- scale(node.traits.COL$collapsed_cropsize)
node.traits.COL$diam                     <- scale(node.traits.COL$diam)
node.traits.COL$nseed                    <- scale(node.traits.COL$nseed)
node.traits.COL$sunken                   <- scale(node.traits.COL$sunken)
node.traits.COL$oneseedw                 <- scale(node.traits.COL$oneseedw)
node.traits.COL$sunken                   <- scale(node.traits.COL$sunken)
node.traits.COL$neighboiurhood_cropsize  <- scale(node.traits.COL$neighboiurhood_cropsize)
node.traits.COL$n_neigh                  <- scale(node.traits.COL$n_neigh)
#OJI
node.traits.OJI$d1                       <- scale(node.traits.OJI$d1)
node.traits.OJI$h                        <- scale(node.traits.OJI$h)
node.traits.OJI$collapsed_cropsize       <- scale(node.traits.OJI$collapsed_cropsize)
node.traits.OJI$diam                     <- scale(node.traits.OJI$diam)
node.traits.OJI$nseed                    <- scale(node.traits.OJI$nseed)
node.traits.OJI$sunken                   <- scale(node.traits.OJI$sunken)
node.traits.OJI$oneseedw                 <- scale(node.traits.OJI$oneseedw)
node.traits.OJI$sunken                   <- scale(node.traits.OJI$sunken)
node.traits.OJI$neighboiurhood_cropsize  <- scale(node.traits.OJI$neighboiurhood_cropsize)
node.traits.OJI$n_neigh                  <- scale(node.traits.OJI$n_neigh)
#MAR
node.traits.MAR$d1                       <- scale(node.traits.MAR$d1)
node.traits.MAR$h                        <- scale(node.traits.MAR$h)
node.traits.MAR$collapsed_cropsize       <- scale(node.traits.MAR$collapsed_cropsize)
node.traits.MAR$diam                     <- scale(node.traits.MAR$diam)
node.traits.MAR$nseed                    <- scale(node.traits.MAR$nseed)
node.traits.MAR$sunken                   <- scale(node.traits.MAR$sunken)
node.traits.MAR$oneseedw                 <- scale(node.traits.MAR$oneseedw)
node.traits.MAR$sunken                   <- scale(node.traits.MAR$sunken)
node.traits.MAR$neighboiurhood_cropsize  <- scale(node.traits.MAR$neighboiurhood_cropsize)
node.traits.MAR$n_neigh                  <- scale(node.traits.MAR$n_neigh)


# I assign the attributes to the graph object by creating an attribute matrix in net.g

#Big-picture

V(net.int)$area                       <-node.traits$area
V(net.int)$h                          <-node.traits$h
V(net.int)$d1                         <-node.traits$d1
V(net.int)$oneseedw                   <-node.traits$oneseedw
V(net.int)$collapsed_cropsize         <-node.traits$collapsed_cropsize
V(net.int)$nseed                      <-node.traits$nseed
V(net.int)$diam                       <-node.traits$diam 
V(net.int)$sunken                     <-node.traits$sunken
V(net.int)$neighboiurhood_cropsize    <-node.traits$neighboiurhood_cropsize
V(net.int)$n_neigh                    <-node.traits$n_neigh

#COL

V(net.COL)$h                          <-node.traits.COL$h
V(net.COL)$d1                         <-node.traits.COL$d1
V(net.COL)$oneseedw                   <-node.traits.COL$oneseedw
V(net.COL)$collapsed_cropsize         <-node.traits.COL$collapsed_cropsize
V(net.COL)$nseed                      <-node.traits.COL$nseed
V(net.COL)$diam                       <-node.traits.COL$diam 
V(net.COL)$sunken                     <-node.traits.COL$sunken
V(net.COL)$neighboiurhood_cropsize    <-node.traits.COL$neighboiurhood_cropsize
V(net.COL)$n_neigh                    <-node.traits.COL$n_neigh

#OJI

V(net.OJI)$h                          <-node.traits.OJI$h
V(net.OJI)$d1                         <-node.traits.OJI$d1
V(net.OJI)$oneseedw                   <-node.traits.OJI$oneseedw
V(net.OJI)$collapsed_cropsize         <-node.traits.OJI$collapsed_cropsize
V(net.OJI)$nseed                      <-node.traits.OJI$nseed
V(net.OJI)$diam                       <-node.traits.OJI$diam 
V(net.OJI)$sunken                     <-node.traits.OJI$sunken
V(net.OJI)$neighboiurhood_cropsize    <-node.traits.OJI$neighboiurhood_cropsize
V(net.OJI)$n_neigh                    <-node.traits.OJI$n_neigh

#MAR

V(net.MAR)$h                          <-node.traits.MAR$h
V(net.MAR)$d1                         <-node.traits.MAR$d1
V(net.MAR)$oneseedw                   <-node.traits.MAR$oneseedw
V(net.MAR)$collapsed_cropsize         <-node.traits.MAR$collapsed_cropsize
V(net.MAR)$nseed                      <-node.traits.MAR$nseed
V(net.MAR)$diam                       <-node.traits.MAR$diam 
V(net.MAR)$sunken                     <-node.traits.MAR$sunken
V(net.MAR)$neighboiurhood_cropsize    <-node.traits.MAR$neighboiurhood_cropsize
V(net.MAR)$n_neigh                    <-node.traits.MAR$n_neigh
```

# Set up graph matrices for models

After creating the igraph object with the information of each associated node, I have to create an adjacency matrix from the igraph object before getting the analogous network object (NETWORK object). From the igraph object, I also extracted all the plant attribute variables to set vertex attributes (nodes) in the network object. ERGMs work with network objects.

```{r Set up matrices for models, echo=TRUE, message= FALSE, warning= FALSE, }

# Create adjacency matrix of igraph object
mat.int <- get.adjacency(net.int, attr = "weight")
mat.col<-  get.adjacency(net.COL, attr = "weight")
mat.oji<-  get.adjacency(net.OJI, attr = "weight")
mat.mar<-  get.adjacency(net.MAR, attr = "weight")


#Create a dataframe with the attributes
v.attrs    <- get.data.frame(net.int, what="vertices")[1:105,]
v.attrsCOL <- get.data.frame(net.COL, what="vertices")[1:35,]
v.attrsOJI <- get.data.frame(net.OJI, what="vertices")[1:35,]
v.attrsMAR <- get.data.frame(net.MAR, what="vertices")[1:35,]

# I create the network object for the model - here "bipartite" = number of plants in the network.
red.big <- network::as.network(as.matrix(mat.int), directed=FALSE, bipartite=105, ignore.eval=FALSE, names.eval='weight') 
red.col <- network::as.network(as.matrix(mat.col), directed=FALSE, bipartite=35,  ignore.eval=FALSE, names.eval='weight') 
red.oji <- network::as.network(as.matrix(mat.oji), directed=FALSE, bipartite=35,  ignore.eval=FALSE, names.eval='weight') 
red.mar <- network::as.network(as.matrix(mat.mar), directed=FALSE, bipartite=35,  ignore.eval=FALSE, names.eval='weight') 

#I set the attributes of the dataframe v.attrs to the netw

#Big-
network::set.vertex.attribute(red.big, "area",                    v.attrs$area) 
network::set.vertex.attribute(red.big, "d1",                      v.attrs$d1)
network::set.vertex.attribute(red.big, "h",                       v.attrs$h)
network::set.vertex.attribute(red.big, "collapsed_cropsize",      v.attrs$collapsed_cropsize)
network::set.vertex.attribute(red.big, "neighboiurhood_cropsize", v.attrs$neighboiurhood_cropsize)
network::set.vertex.attribute(red.big, "n_neigh",                 v.attrs$n_neigh)
network::set.vertex.attribute(red.big, "nseed",                   v.attrs$nseed)
network::set.vertex.attribute(red.big, "diam",                    v.attrs$diam)
network::set.vertex.attribute(red.big, "sunken",                  v.attrs$sunken)
network::set.vertex.attribute(red.big, "oneseedw",                v.attrs$oneseedw)
#COL
network::set.vertex.attribute(red.col, "d1",                      v.attrsCOL$d1)
network::set.vertex.attribute(red.col, "h",                       v.attrsCOL$h)
network::set.vertex.attribute(red.col, "collapsed_cropsize",      v.attrsCOL$collapsed_cropsize)
network::set.vertex.attribute(red.col, "neighboiurhood_cropsize", v.attrsCOL$neighboiurhood_cropsize)
network::set.vertex.attribute(red.col, "n_neigh",                 v.attrsCOL$n_neigh)
network::set.vertex.attribute(red.col, "nseed",                   v.attrsCOL$nseed)
network::set.vertex.attribute(red.col, "diam",                    v.attrsCOL$diam)
network::set.vertex.attribute(red.col, "sunken",                  v.attrsCOL$sunken)
network::set.vertex.attribute(red.col, "oneseedw",                v.attrsCOL$oneseedw)
#OJI
network::set.vertex.attribute(red.oji, "d1",                      v.attrsOJI$d1)
network::set.vertex.attribute(red.oji, "h",                       v.attrsOJI$h)
network::set.vertex.attribute(red.oji, "collapsed_cropsize",      v.attrsOJI$collapsed_cropsize)
network::set.vertex.attribute(red.oji, "neighboiurhood_cropsize", v.attrsOJI$neighboiurhood_cropsize)
network::set.vertex.attribute(red.oji, "n_neigh",                 v.attrsOJI$n_neigh)
network::set.vertex.attribute(red.oji, "nseed",                   v.attrsOJI$nseed)
network::set.vertex.attribute(red.oji, "diam",                    v.attrsOJI$diam)
network::set.vertex.attribute(red.oji, "sunken",                  v.attrsOJI$sunken)
network::set.vertex.attribute(red.oji, "oneseedw",                v.attrsOJI$oneseedw)
#MAR
network::set.vertex.attribute(red.mar, "d1",                      v.attrsMAR$d1)
network::set.vertex.attribute(red.mar, "h",                       v.attrsMAR$h)
network::set.vertex.attribute(red.mar, "collapsed_cropsize",      v.attrsMAR$collapsed_cropsize)
network::set.vertex.attribute(red.mar, "neighboiurhood_cropsize", v.attrsMAR$neighboiurhood_cropsize)
network::set.vertex.attribute(red.mar, "n_neigh",                 v.attrsMAR$n_neigh)
network::set.vertex.attribute(red.mar, "nseed",                   v.attrsMAR$nseed)
network::set.vertex.attribute(red.mar, "diam",                    v.attrsMAR$diam)
network::set.vertex.attribute(red.mar, "sunken",                  v.attrsMAR$sunken)
network::set.vertex.attribute(red.mar, "oneseedw",                v.attrsMAR$oneseedw)
```

# ERGM MODELS

The workflow is as follows:

1- Fit the best possible "big picture" model where I will not use the neighborhood variables but the area variables. It will be adjusted in a hierarchical and AIC based way.  
2- Transfer this model to the small networks, to see how sustained the trends are, and if they vary between sites, and to evaluate the effect of the neighborhood context.

```{r setting models, echo=TRUE, message= FALSE, warning= FALSE}
library(ergm.count)

# Model formulation

# Empty model
model.0 <- formula(red.big ~ sum)
                        #+ b1factor("area", base = 1, form="sum")
                        #+ b1cov("d1", form= "sum")
                        #+ b1cov("h", form= "sum")
                        #+ b1cov("collapsed_cropsize", form= "sum")
                        #+ b1cov("diam", form= "sum")
                        #+ b1cov("nseed", form= "sum")
                        #+ b1cov("sunken", form= "sum")
                        #+ b1cov("oneseedw", form= "sum")
# Area model 
#1 = COL
#2 = OJI
#3 = MAR
model.1<- formula(red.big ~ sum
                         + b1factor("area", base = 1, form="sum"))
                        #+ b1cov("d1", form= "sum")
                        #+ b1cov("h", form= "sum")
                        #+ b1cov("collapsed_cropsize", form= "sum")
                        #+ b1cov("diam", form= "sum")
                        #+ b1cov("nseed", folevels()
                        #+ b1cov("sunken", form= "sum")
                        #+ b1cov("oneseedw", form= "sum")
# General-plant model
model.2<- formula(red.big ~ sum
                        #+ b1factor("area", base = 1, form="sum")
                         + b1cov("d1", form= "sum")
                         + b1cov("h", form= "sum")
                         + b1cov("collapsed_cropsize", form= "sum"))
                        #+ b1cov("diam", form= "sum")
                        #+ b1cov("nseed", form= "sum")
                        #+ b1cov("sunken", form= "sum")
                        #+ b1cov("oneseedw", form= "sum")
# Cone-model
model.3<- formula(red.big ~ sum
                        #+ b1factor("area", base = 1, form="sum")
                        #+ b1cov("d1", form= "sum")
                        #+ b1cov("h", form= "sum")
                        #+ b1cov("collapsed_cropsize", form= "sum")
                         + b1cov("diam", form= "sum")
                         + b1cov("nseed", form= "sum")
                         + b1cov("sunken", form= "sum")
                         + b1cov("oneseedw", form= "sum"))
# Cone + plant model
model.4<- formula(red.big ~ sum
                        #+ b1factor("area", base = 1, form="sum")
                         + b1cov("d1", form= "sum")
                         + b1cov("h", form= "sum")
                         + b1cov("collapsed_cropsize", form= "sum")
                         + b1cov("diam", form= "sum")
                         + b1cov("nseed", form= "sum")
                         + b1cov("sunken", form= "sum")
                         + b1cov("oneseedw", form= "sum"))
# Area + plant model
model.5<- formula(red.big ~ sum
                        + b1factor("area", base = 1, form="sum")
                         + b1cov("d1", form= "sum")
                         + b1cov("h", form= "sum")
                         + b1cov("collapsed_cropsize", form= "sum"))
                         #+ b1cov("diam", form= "sum")
                         #+ b1cov("nseed", form= "sum")
                         #+ b1cov("sunken", form= "sum")
                         #+ b1cov("oneseedw", form= "sum"))
# Area + cone model
model.6<- formula(red.big ~ sum
                        + b1factor("area", base = 1, form="sum")
                         #+ b1cov("d1", form= "sum")
                         #+ b1cov("h", form= "sum")
                         #+ b1cov("collapsed_cropsize", form= "sum")
                         + b1cov("diam", form= "sum")
                         + b1cov("nseed", form= "sum")
                         + b1cov("sunken", form= "sum")
                         + b1cov("oneseedw", form= "sum"))


# Full model
model.7<- formula(red.big ~ sum
                         + b1factor("area", base = 1, form="sum")
                         + b1cov("d1", form= "sum")
                         + b1cov("h", form= "sum")
                         + b1cov("collapsed_cropsize", form= "sum")
                         + b1cov("diam", form= "sum")
                         + b1cov("nseed", form= "sum")
                         + b1cov("sunken", form= "sum")
                         + b1cov("oneseedw", form= "sum"))
```

# Model fitting

```{r Model fitting, , message= FALSE, warning=FALSE}

set.seed(99) 
require(ergm.count)
ergm.model.0 <- ergm(model.0, response = "weight", reference= ~Poisson)
ergm.model.1 <- ergm(model.1, response = "weight", reference= ~Poisson)
ergm.model.2 <- ergm(model.2, response = "weight", reference= ~Poisson)
ergm.model.3 <- ergm(model.3, response = "weight", reference= ~Poisson)
ergm.model.4 <- ergm(model.4, response = "weight", reference= ~Poisson)
ergm.model.5 <- ergm(model.5, response = "weight", reference= ~Poisson)
ergm.model.6 <- ergm(model.6, response = "weight", reference= ~Poisson)
ergm.model.7 <- ergm(model.7, response = "weight", reference= ~Poisson)
```

```{r Model summary}
summary(ergm.model.0) # Modelo vacío                 AIC = -5630    
summary(ergm.model.1) # Modelo area                  AIC = -5790    
summary(ergm.model.2) # Modelo planta                AIC = -5890    
summary(ergm.model.3) # Modelo cono                  AIC = -5981   
summary(ergm.model.4) # Modelo planta + cono         AIC = -6072*** 
summary(ergm.model.5) # Modelo area + planta         AIC = -5918  
summary(ergm.model.6) # Modelo area + cono           AIC = -5917  
summary(ergm.model.7) # Modelo completo              AIC = -6072  
```

```{r Models comparison plots}

BIG_PICTURE_MODELNAMES<-c("AREA MODEL","PLANT MODEL","CONE MODEL","PLANT+CONE MODEL WIN","AREA + PLANT MODEL", "AREA + CONE MODEL", "FULL MODEL WIN")
require(jtools)
plot_summs(ergm.model.1,ergm.model.2,ergm.model.3,ergm.model.4,ergm.model.5,ergm.model.6,ergm.model.7, model.names = BIG_PICTURE_MODELNAMES,omit.coefs = "sum", scale = TRUE )
```

```{r bEST big-picture model}
summary(ergm.model.4) #Table 1
library(jtools)
plot_summs(ergm.model.4,omit.coefs = "sum", scale = TRUE )
```

# Per-stand model formulation
```{r Per-stand model formulation}
library(ergm.count)



# COL
model.COL <- formula(red.col ~ sum
                        + b1cov("d1", form= "sum")
                        + b1cov("h", form= "sum")
                        + b1cov("collapsed_cropsize", form= "sum")
                        + b1cov("diam", form= "sum")
                        + b1cov("nseed", form= "sum")
                        + b1cov("sunken", form= "sum")
                        + b1cov("oneseedw", form= "sum")
                        + b1cov("n_neigh", form= "sum")
                        + b1cov("neighboiurhood_cropsize", form= "sum"))

# OJI
model.OJI <- formula(red.oji ~ sum
                        + b1cov("d1", form= "sum")
                        + b1cov("h", form= "sum")
                        + b1cov("collapsed_cropsize", form= "sum")
                        + b1cov("diam", form= "sum")
                        + b1cov("nseed", form= "sum")
                        + b1cov("sunken", form= "sum")
                        + b1cov("oneseedw", form= "sum")
                        + b1cov("n_neigh", form= "sum")
                        + b1cov("neighboiurhood_cropsize", form= "sum"))
# MAR
model.MAR <- formula(red.mar ~ sum
                        + b1cov("d1", form= "sum")
                        + b1cov("h", form= "sum")
                        + b1cov("collapsed_cropsize", form= "sum")
                        + b1cov("diam", form= "sum")
                        + b1cov("nseed", form= "sum")
                        + b1cov("sunken", form= "sum")
                        + b1cov("oneseedw", form= "sum")
                        + b1cov("n_neigh", form= "sum")
                        + b1cov("neighboiurhood_cropsize", form= "sum"))
```

```{r Per-stand model fitting, message= FALSE, warning=FALSE}
set.seed(99)
require(ergm.count)
ergm.model.COL <- ergm(model.COL, response = "weight", reference= ~Poisson)
ergm.model.OJI <- ergm(model.OJI, response = "weight", reference= ~Poisson)
ergm.model.MAR <- ergm(model.MAR, response = "weight", reference= ~Poisson)
```

```{r Models summary}
summary(ergm.model.COL)                                                       
summary(ergm.model.OJI) 
summary(ergm.model.MAR)          

AREANAMES<-c("SABINAR DE COLONIZACIÓN", "SABINAR DEL OJILLO", "SABINAR DEL MARQUES")
library(jtools)
plot_coefs(ergm.model.COL,ergm.model.OJI,ergm.model.MAR, model.names = AREANAMES,omit.coefs = "sum", scale = TRUE) 
```

```{r plotting estimates}
#COL: LINK (62.47%), PLANT (7.127%) CONE (26.845 %) NEIGH (3.554%)
#OJI: LINK (49.012%), PLANT (28.113%) CONE ( 10.480%) NEIGH ( 12.394%)
#MAR: LINK (46.696%), PLANT (16.034%) CONE (26.08268 %) NEIGH (11.185%)


area_ergm_df5 <- data.frame(area=c("SABCOL","SABCOL","SABCOL","SABCOL","SABOJI","SABOJI","SABOJI","SABOJI","SABMAR","SABMAR","SABMAR","SABMAR"),level= c("Cone quality traits","dPlant phenotype","Neighbourhood attribues","aLink distribution","Cone quality traits","dPlant phenotype","Neighbourhood attribues","aLink distribution","Cone quality traits","dPlant phenotype","Neighbourhood attribues","aLink distribution"), value= c(26.845,7.127,3.554,62.47,10.480,28.113,12.394,49.012,26.082,16.034,11.185,46.696))
area_ergm_df5$area<-recode_factor(area_ergm_df5$area, SABMAR ="ASABMAR", SABOJI = "BSABOJI")

plot5<-ggplot(area_ergm_df5, aes(x = area, y = value, fill = level)) + 
  geom_bar(stat = "identity", color = "black") +   scale_fill_manual(values = c("#ffff99","#fdc086", "#7fc97f", "#beaed4")) + theme_bw()+ labs(y = " CONTRIBUTION TO COMBINED VARIABLES TO TOTAL TOTAL VALUE OF ESTIMATES", x = "AREA")

plot5
```