---
title: "Individual_networks and plots"
author: "Jorge"
date: "3/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Package loading, include = FALSE}
library(ggplot2)
library(reshape2)
library(readr)
library(patchwork)
library(vegan)
library(permute)
library(lattice)
library(grid)
library(tibble)
library(ggnet)
library(intergraph)
library(RColorBrewer)
library(GGally)
library(network)
library(sna)
library(dplyr)
library(bipartite)
library(gridGraphics)
library(magrittr)
library(igraph)
library(wesanderson)
library(ca)
library(usethis)
library(devtools)
#devtools::install_github("pedroj/bipartite_plots")
library(ggbipart)
library(dplyr)
library(bootstrap)
library(sampling)
library(textshape)
library(nFactors)
library(ade4)
library(vegan)
library(devtools)
devtools::install_github("pakillo/effectiveness_pckg", force=TRUE)
library(effect.lndscp)
```

#Interaction data loading
```{r Data loading + data as numeric}
data <- read_delim ("~/Documents/GitHub/JEcology_Isla2022/data/dataset.csv", ";", escape_double = FALSE, trim_ws = TRUE)

data<-column_to_rownames(data, loc = 1 )%>% 
  mutate(area = factor(area, levels = c("SABCOL", "SABOJI", "SABMAR"))) # tree identification to row names.

#Frequency of appearance of interactions as numerical variables. 
data$fa_4cone_chl <- as.numeric(data$fa_4cone_chl)
data$fa_apo <- as.numeric(data$fa_apo)
data$fa_mus <- as.numeric(data$fa_mus)
data$fa_mesophleps <- as.numeric(data$fa_mesophleps)
data$fa_elachista <- as.numeric(data$fa_elachista)
data$fa_nanodiscus <- as.numeric(data$fa_nanodiscus)
data$fa_megastigmus <- as.numeric(data$fa_megastigmus)
```

```{r Interaction matrix creation}
int<-data[,c(1,17,18,19,20,21,22,23)] #Filtering interactions of the raw dataset

#Splitting dataset by area
intALL<-int[,-1,]      #Big-picture
intCOL<-int[1:35,-1]   #Colonization front stand
intMAR<-int[36:70,-1]  #Intermediate maturity stand
intOJI<-int[71:105,-1] #Mature stand


intALL<-as.matrix(intALL)  #Datasets as a matrix
#dim(intALL) #Matrix size check
intCOL<-as.matrix(intCOL)  #Datasets as a matrix
#dim(intCOL) #Matrix size check
intOJI<-as.matrix(intOJI)  #Datasets as a matrix
#dim(intOJI) #Matrix size check
intMAR<-as.matrix(intMAR)  #Datasets as a matrix
#dim(intMAR) #Matrix size check
```

```{r Networks preview}
#Networks preview

plotweb(intALL, col.interaction = 'snow3', col.high = 'black', col.low = "green")
#visweb(intALL, type = "nested")
plotweb(intCOL, col.interaction = 'snow3', col.high = 'black', col.low = "#35978f")
#visweb(intCOL, type = "nested")
plotweb(intOJI, col.interaction = 'snow3', col.high = 'black', col.low = '#dfc27d')
#visweb(intOJI, type = "nested")
plotweb(intMAR, col.interaction = 'snow3', col.high = 'black', col.low = '#8c510a')
#visweb(intMAR, type = "nested")
```

#Now I construct-plot a bipartite weighted individual-based network (interactions between individual plants and antagonist species based on occurrence frequency in sampling), using ggnet.

```{r vis.BIPARTITE}
intALL.m1 = network (intALL, matrix.type = "bipartite", ignore.eval= FALSE, names.eval = "weights")

# Colour fixed

col = c("actor"= "#4dac26", "event" = "#dfc27d")

network.vertex.names(intALL.m1)[106:112] <- c("CHL", "APO", "MUS", "MES", "ELA", "NAN", "MEG")
#network.vertex.names(intALL.m1)

ALL.net<-bip_ggnet(intALL.m1, as.matrix(intALL), 
                   size = 0, 
                   shape ="mode", 
                   palette = col, 
                   color = "mode", 
                   layout.exp = 0.1) + 
    geom_point(aes(color= col), size= 10,
                         color= "white") +
          geom_point(aes(color= color), size= 10,
                         alpha= 0.1) +
          geom_point(aes(color= color), size= 8) +
          geom_text(aes(label= network.vertex.names(intALL.m1)),
                        color= "white", size= 2,
                        fontface="bold") +
          guides(color= FALSE) +
          theme(legend.position="none")
ALL.net
```

#Now each stand separately
#SABCOL
```{r}
intCOL.m1 = network (intCOL, matrix.type = "bipartite", ignore.eval= FALSE, names.eval = "weights")

sabcolors <- c("SABCOL"="#35978f", "SABOJI"="#dfc27d", "SABMAR"="#8c510a")

col = c("actor" = "#35978f", "event" = "black")


network.vertex.names(intCOL.m1)[36:42] <- c("CHL", "APO", "MUS", "MES", "ELA", "NAN", "MEG")

COL.net<-bip_ggnet(intCOL.m1, as.matrix(intCOL), 
                   size = 0, 
                   shape ="mode", 
                   palette = col, 
                   color = "mode", 
                   layout.exp = 0.1) + 
    geom_point(aes(color= color), size= 12,
                         color= "grey") +
          geom_point(aes(color= color), size= 11,
                         alpha= 0.5) +
          geom_point(aes(color= color), size= 10.5) +
          geom_text(aes(label= network.vertex.names(intCOL.m1)),
                        color= "white", size= 2.5,
                        fontface="bold") +
          guides(color= FALSE) +
          theme(legend.position="none")
COL.net
```

#SABOJI
```{r}
intOJI.m1 = network (intOJI, matrix.type = "bipartite", ignore.eval= FALSE, names.eval = "weights")

col = c("actor" = "#dfc27d", "event" = "black")
set.seed(92)

network.vertex.names(intOJI.m1)[36:42] <- c("CHL", "APO", "MUS", "MES", "ELA", "NAN", "MEG")

OJI.net<-bip_ggnet(intOJI.m1, as.matrix(intOJI), 
                   size = 0, 
                   shape ="mode", 
                   palette = col, 
                   color = "mode", 
                   layout.exp = 0.1) + 
    geom_point(aes(color= color), size= 12,
                         color= "grey") +
          geom_point(aes(color= color), size= 11,
                         alpha= 0.5) +
          geom_point(aes(color= color), size= 10.5) +
          geom_text(aes(label= network.vertex.names(intOJI.m1)),
                        color= "white", size= 2.5,
                        fontface="bold") +
          guides(color= FALSE) +
          theme(legend.position="none")
OJI.net
```
 
#SABMAR
```{r}
intMAR.m1 = network (intMAR, matrix.type = "bipartite", ignore.eval= FALSE, names.eval = "weights")

col = c("actor" = "#8c510a", "event" = "black")

network.vertex.names(intMAR.m1)[36:42] <- c("CHL", "APO", "MUS", "MES", "ELA", "NAN", "MEG")
set.seed(92)
MAR.net<-bip_ggnet(intMAR.m1, as.matrix(intMAR), 
                   size = 0, 
                   shape ="mode", 
                   palette = col, 
                   color = "mode", 
                   layout.exp = 0.1) + 
    geom_point(aes(color= color), size= 12,
                         color= "grey") +
          geom_point(aes(color= color), size= 11,
                         alpha= 0.5) +
          geom_point(aes(color= color), size= 10.5) +
          geom_text(aes(label= network.vertex.names(intMAR.m1)),
                        color= "white", size= 2.5,
                        fontface="bold") +
          guides(color= FALSE) +
          theme(legend.position="none")
MAR.net

#3 PLOTS TOGETHER 
library(patchwork)
MAR.net/OJI.net/COL.net
```

```{r NETEORKS METRICS COMPUTATION}

#Rounding values to reduce computation time:

intALL <- round(intALL*100, digits = 0)
intCOL <- round(intCOL*100, digits = 0)
intOJI <- round(intOJI*100, digits = 0)
intMAR <- round(intMAR*100, digits = 0)

#Metrics estimation

#COL
intCOLmetrics<-networklevel(intCOL, weighted=TRUE,index = c("weighted connectance", "weighted NODF","H2"),nrep = 100) # Network level metrics
intCOLmetricspecies<-specieslevel(intCOL,level="higher",index = c("degree","species strength")) #Node level metrics (animals)                    
intCOLmetricPLANTS<-specieslevel(intCOL,level="lower",index = c("degree","species strength","closeness")) #Node level metrics (plants)     

#OJI
intOJImetrics<-networklevel(intOJI, weighted=TRUE,index = c("weighted connectance", "weighted NODF","H2"),nrep = 100) # Network level metrics
intOJImetricspecies<-specieslevel(intOJI,level="higher",index = c("degree","species strength"))  #Node level metrics (animals)       
intOJImetricPLANTS<-specieslevel(intOJI,level="lower",index = c("degree","species strength","closeness")) #Node level metrics (plants)  


#MAR
intMARmetrics<-networklevel(intMAR, weighted=TRUE,index = c("weighted connectance", "weighted NODF","H2"),nrep = 100)  # Network level metrics
intMARmetricspecies<-specieslevel(intMAR,level="higher",index = c("degree","species strength")) #Node level metrics (animals)  
intMARmetricPLANTS<-specieslevel(intMAR,level="lower",index = c("degree","species strength","closeness")) #Node level metrics (plants)  

#ALL
intALLmetricPLANTS<-specieslevel(intALL,level="lower",index = "species strength") #Node level metrics (plants)  
intALLmetricPLANTS
```

```{r Creating dataframes for plots}

COL<-c(rep("SABCOL", 7))
OJI<-c(rep("SABOJI", 7))
MAR<-c(rep("SABMAR", 7))
area<-c(COL,OJI,MAR)

#Creating dataframe for plants
new.areaCOL<-c(rep("SABCOL", 34))
new.areaOJI<-c(rep("SABOJI", 35))
new.areaMAR<-c(rep("SABMAR", 34))
new.area<-c(new.areaCOL,new.areaOJI,new.areaMAR,new.areaCOL,new.areaOJI,new.areaMAR)

#For animals
degree<-rep("degree",21)
speciesstrength<-rep("species strength",21)
metric<-c(degree,speciesstrength)

#For plants
metric2degree<-c(rep("degree",103))
metric2speciesstrength<-c(rep("speciesstrength",103))
new.metrics<-c(metric2degree,metric2speciesstrength)

#For animals
animal.names<-row.names(intCOLmetricspecies)
animal<-rep(animal.names,6)


#For palnts
colo<-row.names(intCOLmetricPLANTS)
ojil<-row.names(intOJImetricPLANTS)
marq<-row.names(intMARmetricPLANTS)
names<-c(colo,ojil,marq,colo,ojil,marq)

#For species
values<- c((intCOLmetricspecies$degree), (intOJImetricspecies$degree),(intMARmetricspecies$degree),(intCOLmetricspecies$species.strength),(intOJImetricspecies$species.strength),(intMARmetricspecies$species.strength))

#For plants
values2<-c((intCOLmetricPLANTS$degree),(intOJImetricPLANTS$degree),(intMARmetricPLANTS$degree),(intCOLmetricPLANTS$species.strength),(intOJImetricPLANTS$species.strength),(intMARmetricPLANTS$species.strength))

dataframespecieslevel<-data.frame(AREA=area, Metric=metric, Species = animal, Value = values)
dataframeplantlevel<-data.frame(AREA=new.area, Metric=new.metrics, Species = names, Value = values2)
```

#Modularity computation
```{r Modularity}
intALLt<-t(intALL)
modintALL <- computeModules(intALLt, method="Beckett", deep= FALSE, deleteOriginalFiles= FALSE, steps= 1000, tolerance= 1e-10, experimental= FALSE, forceLPA= FALSE)
modintALL

intCOLt<-t(intCOL)
modintCOL <- computeModules(intCOLt, method="Beckett", deep= FALSE, deleteOriginalFiles= FALSE, steps= 1000, tolerance= 1e-10, experimental= FALSE, forceLPA= FALSE)
modintCOL


intOJIt<-t(intOJI)
modintOJI <- computeModules(intOJIt, method="Beckett", deep= FALSE, deleteOriginalFiles= FALSE, steps= 1000, tolerance= 1e-10, experimental= FALSE, forceLPA= FALSE)
modintOJI

intMARt<-t(intMAR)
modintMAR <- computeModules(intMARt, method="Beckett", deep= FALSE, deleteOriginalFiles= FALSE, steps= 1000, tolerance= 1e-10, experimental= FALSE, forceLPA= FALSE)
modintMAR

# Modularity intALL likelyhood = 0.3457235
# Modularity intCOL likelyhood = 0.2506048
# Modularity intOJI likelyhood = 0.2822584
# Modularity intMAR likelyhood = 0.3320767

plotModuleWeb(modintALL)
plotModuleWeb(modintCOL)
plotModuleWeb(modintOJI)
plotModuleWeb(modintMAR)
```

```{r Modularity significance}

#For COL
czCOLplants<-czvalues(modintCOL, weighted=TRUE, level="higher")
czCOLplants
czCOLanimal<-czvalues(modintCOL, weighted=TRUE, level="lower")
czCOLanimal

mymatCOL <- intCOLt
require(bipartite)

mod_obsCOL <-  0.2506048

Msig <- function (mat, mlike)  {

  
    # mat is the input matrix for which M is tested
    # mlike is the observed mean M value
    
    nulls <- nullmodel(mymatCOL, N=100, method=3)
    modules.nulls <- sapply(nulls, computeModules)
    like.nulls <- sapply(modules.nulls, function(x) x@likelihood)
    z <- (mlike - mean(like.nulls))/sd(like.nulls)
    p <- 2*pnorm(-abs(z))
    cat("\n\n","P value for modularity M= ", mod_obsCOL, "\n", "\n\n",
        "zeta=  ", z,
        "P=  ",format(p, scientific = T),"\n\n")
        } 

Msig(mymatCOL, mod_obsCOL)

#For OJI
czOJIplants<-czvalues(modintOJI, weighted=TRUE, level="higher")
czOJIplants
czOJIanimal<-czvalues(modintOJI, weighted=TRUE, level="lower")
czOJIanimal

mymatOJI <- intOJIt
require(bipartite)

mod_obsOJI <-  0.2822584

Msig <- function (mat, mlike)  {

  
    # mat is the input matrix for which M is tested
    # mlike is the observed mean M value
    
    nulls <- nullmodel(mymatOJI, N=100, method=3)
    modules.nulls <- sapply(nulls, computeModules)
    like.nulls <- sapply(modules.nulls, function(x) x@likelihood)
    z <- (mlike - mean(like.nulls))/sd(like.nulls)
    p <- 2*pnorm(-abs(z))
    cat("\n\n","P value for modularity M= ", mod_obsOJI, "\n", "\n\n",
        "zeta=  ", z,
        "P=  ",format(p, scientific = T),"\n\n")
        } 

Msig(mymatOJI, mod_obsOJI)

#For MAR
czMARplants<-czvalues(modintMAR, weighted=TRUE, level="higher")
czMARplants
czMARanimal<-czvalues(modintMAR, weighted=TRUE, level="lower")
czMARanimal

mymatMAR <- intMARt
require(bipartite)

mod_obsMAR <- 0.3320767

Msig <- function (mat, mlike)  {

  
    # mat is the input matrix for which M is tested
    # mlike is the observed mean M value
    
    nulls <- nullmodel(mymatMAR, N=100, method=3)
    modules.nulls <- sapply(nulls, computeModules)
    like.nulls <- sapply(modules.nulls, function(x) x@likelihood)
    z <- (mlike - mean(like.nulls))/sd(like.nulls)
    p <- 2*pnorm(-abs(z))
    cat("\n\n","P value for modularity M= ", mod_obsMAR, "\n", "\n\n",
        "zeta=  ", z,
        "P=  ",format(p, scientific = T),"\n\n")
        } 

Msig(mymatMAR, mod_obsMAR)
```

Results:
#INTCOL

Weighted Connectance = 0.307661 
zeta=   -7.450015
P=    9.332962e-14 

WNODF N= 39.0702  
zeta=   -3.024829 
P=   2.487736e-03 


H2=  0.2728968 
zeta=   16.07616 
P=   3.749227e-58 

#INTOJI

Weighted connectance C=  0.2577812 
zeta=   -15.73958 
P=   8.097865e-56 

WNODF N=  31.29092 
zeta=   -5.081784 
P=   3.739062e-07 

H2=  0.3173446 
zeta=   18.023 
P=   1.285816e-72 


#INTMAR
Weighted connectance C=  0.2356121 
zeta=   -8.734931
P=   2.438057e-18 

WNODF N=  27.96062 
zeta=   -7.938668 
P=   2.043635e-15 

H2=  0.3234387 
zeta=   17.92492 
P=   7.536192e-72 

## Bootstrap estimates of network parameters
We estimated the confidence intervals by resampling interaction networks from the different methods and computing their average, SE, and CIs.
```{r CIs_INTCOL}
#here
require(bootstrap)
require(bipartite)
require(sampling)
#
# Bootstrap loop to create the boot matrices --------------

mat <- intCOL
mat<-as.data.frame(mat)
intCobs<- as.vector(networklevel(mat, 
    			  index = c("weighted connectance",
    			  		    "weighted NODF", "H2")))

# Resampling plan for bootstrapping n=99 adjacency matrices.
resamp <- 99                # Number of bootstrap samples required
intCmetrics_boot<- NULL

# The loop. PUT THIS IN A BOOT LOOP 
for (i in 1:resamp) {
    mat1 <- sample_frac(mat, 0.8, replace= T)
   intCmetrics<- as.vector(networklevel(mat1, 
    			  index = c("weighted connectance",
    			  		    "weighted NODF", "H2")))
    intCmetrics_boot<- rbind(intCmetrics_boot, intCmetrics)   
}
	colnames(intCmetrics_boot)<- c("weighted NODF","weighted connectance", "H2")

# Outputs bootstraped parameter differences values as dataframe. -------------
intCOL_boot <- as.data.frame(colMeans(intCmetrics_boot))
rnd.se <- as.vector(apply(intCmetrics_boot,2,sd)/sqrt(resamp)) # SE randomized parameters
intCOL_boot<- cbind(intCOL_boot, rnd.se)

ci1 <-  intCobs-(1.962*intCOL_boot$rnd.se)
ci2 <-  intCobs+(1.962*intCOL_boot$rnd.se)

intCOL_boot<- cbind(intCOL_boot, ci1, ci2)
colnames(intCOL_boot)<- c("mean.boot", "SE", 
								 "CI_low",
								 "CI_high")
intCOL_boot<- cbind(intCobs,intCOL_boot)

#
# Output parameters
# meandf         # Bootstrap mean of parameter values
# SE             # Bootstrap SE for parameter values
# CI_low         # Bootstrap CI (lower) 
# CI_high        # Bootstrap CI (higher) 
intCOL_boot
```

```{r CIs_INTOJI}
require(bootstrap)
require(bipartite)
require(sampling)
# Bootstrap loop to create the boot matrices --------------

mat <- intOJI
mat<-as.data.frame(mat)
intOobs<- as.vector(networklevel(mat, 
    			  index = c("weighted connectance",
    			  		    "weighted NODF","H2")))

# Resampling plan for bootstrapping n=99 adjacency matrices.
resamp <- 99                # Number of bootstrap samples required
intOmetrics_boot<- NULL

# The loop. PUT THIS IN A BOOT LOOP 
for (i in 1:resamp) {
    mat1 <- sample_frac(mat, 0.8, replace= T)
   intOmetrics<- as.vector(networklevel(mat1, 
    			  index = c("weighted connectance",
    			  		    "weighted NODF", "H2")))
    intOmetrics_boot<- rbind(intOmetrics_boot, intOmetrics)   
}
	colnames(intOmetrics_boot)<- c("weighted NODF","weighted connectance", "H2")

# Outputs bootstraped parameter differences values as dataframe. -------------
intOJI_boot <- as.data.frame(colMeans(intOmetrics_boot))
rnd.se <- as.vector(apply(intOmetrics_boot,2,sd)/sqrt(resamp)) # SE randomized parameters
intOJI_boot<- cbind(intOJI_boot, rnd.se)

ci1 <-  intOobs-(1.962*intOJI_boot$rnd.se)
ci2 <-  intOobs+(1.962*intOJI_boot$rnd.se)

intOJI_boot<- cbind(intOJI_boot, ci1, ci2)
colnames(intOJI_boot)<- c("mean.boot", "SE", 
								 "CI_low",
								 "CI_high")
intOJI_boot<- cbind(intOobs,intOJI_boot)

#
# Output parameters
# meandf         # Bootstrap mean of parameter values
# SE             # Bootstrap SE for parameter values
# CI_low         # Bootstrap CI (lower) 
# CI_high        # Bootstrap CI (higher) 
intOJI_boot
```

```{r CIs_INTMAR}
#
require(bootstrap)
require(bipartite)
require(sampling)
#
# Bootstrap loop to create the boot matrices --------------

mat <- intMAR
mat<-as.data.frame(mat)
intMobs<- as.vector(networklevel(mat, 
    			  index = c("weighted connectance",
    			  		    "weighted NODF","H2")))

# Resampling plan for bootstrapping n=99 adjacency matrices.
resamp <- 99                # Number of bootstrap samples required
intMmetrics_boot<- NULL

# The loop. PUT THIS IN A BOOT LOOP 
for (i in 1:resamp) {
    mat1 <- sample_frac(mat, 0.8, replace= T)
   intMmetrics<- as.vector(networklevel(mat1, 
    			  index = c("weighted connectance",
    			  		    "weighted NODF", "H2")))
    intMmetrics_boot<- rbind(intMmetrics_boot, intMmetrics)   
}
	colnames(intMmetrics_boot)<- c("weighted NODF","weighted connectance", "H2")

# Outputs bootstraped parameter differences values as dataframe. -------------
intMAR_boot <- as.data.frame(colMeans(intMmetrics_boot))
rnd.se <- as.vector(apply(intMmetrics_boot,2,sd)/sqrt(resamp)) # SE randomized parameters
intMAR_boot<- cbind(intMAR_boot, rnd.se)

ci1 <-  intMobs-(1.962*intMAR_boot$rnd.se)
ci2 <-  intMobs+(1.962*intMAR_boot$rnd.se)

intMAR_boot<- cbind(intMAR_boot, ci1, ci2)
colnames(intMAR_boot)<- c("mean.boot", "SE", 
								 "CI_low",
								 "CI_high")
intMAR_boot<- cbind(intMobs,intMAR_boot)

#
# Output parameters
# meandf         # Bootstrap mean of parameter values
# SE             # Bootstrap SE for parameter values
# CI_low         # Bootstrap CI (lower) 
# CI_high        # Bootstrap CI (higher) 
intMAR_boot

```

## Functions to load
### Function to estimate M from bootstrapped matrices.
```{r m_boot.function}
# Function for Bootstrap loop to estimate M for resampled matrices. ------------
# USE WITH: m_boot(mymat, myresamp). myresamp defaults to 99.
m_boot <- function (mymat, myresamp= 99)  {
	TIME <- Sys.time()
	# Resampling plan for bootstrapping n=99 adjacency matrices.
	m.boot<- NULL
	# mat is the input matrix for which M is tested
	# mlike is the observed mean M value (in general, mat@likelihood)
	# The loop. PUT THIS IN A BOOT LOOP 
	for (i in 1:myresamp) {
		mat1 <- sample_frac(mymat, 0.8, replace= T)
		mnmetrics <- computeModules(mat1, method="Beckett", 
								   deep= FALSE, deleteOriginalFiles= FALSE, 
								   steps= 1000, tolerance= 1e-10, 
								   experimental= FALSE, forceLPA= FALSE)
		m.boot<- rbind(m.boot, mnmetrics@likelihood)   
	}
	colnames(m.boot)<- c("MBoot") # m.boot saves the M values for bootstrapped 
								  # matrices.
	return(m.boot)
	#
	Sys.time() - TIME
	#
} 

```


```{r COL Modularity CI}
M_COL <- computeModules(intCOL, method="Beckett", deep= FALSE, 
					   deleteOriginalFiles= FALSE, steps= 1000, 
					   tolerance= 1e-10, experimental= FALSE, forceLPA= FALSE)
intCOL<-as.data.frame(intCOL)
M_COL@likelihood

MObs<- M_COL@likelihood

COL_Mboot <- as.data.frame(cbind(MObs, # colMeans(m.boot)))
									 colMeans(m.boot<-m_boot(intCOL, 99))))
rnd.se <- apply(m.boot,2,sd)/sqrt(length(m.boot))   # SE randomized parameters
COL_Mboot<- cbind(COL_Mboot, rnd.se)
ci1 <-  MObs-(1.962*COL_Mboot$rnd.se)
ci2 <-  MObs+(1.962*COL_Mboot$rnd.se)


COL_Mboot<- cbind(COL_Mboot, ci1, ci2)
colnames(COL_Mboot)<- c("MObs", "meanM.boot", "SE", 
								  "CI_low",
								  "CI_high")
#
# Output parameters
# meandf         # Bootstrap mean of parameter values
# SE             # Bootstrap SE for parameter values
# CI_low         # Bootstrap CI (lower) 
# CI_high        # Bootstrap CI (higher) 
COL_Mboot

```

```{r OJI MODULARITY CI}
M_OJI <- computeModules(intOJI, method="Beckett", deep= FALSE, 
					   deleteOriginalFiles= FALSE, steps= 1000, 
					   tolerance= 1e-10, experimental= FALSE, forceLPA= FALSE)
intOJI<-as.data.frame(intOJI)
M_OJI@likelihood

MObs<- M_OJI@likelihood

OJI_Mboot <- as.data.frame(cbind(MObs, # colMeans(m.boot)))
									 colMeans(m.boot<-m_boot(intOJI, 99))))
rnd.se <- apply(m.boot,2,sd)/sqrt(length(m.boot))   # SE randomized parameters
OJI_Mboot<- cbind(OJI_Mboot, rnd.se)
ci1 <-  MObs-(1.962*OJI_Mboot$rnd.se)
ci2 <-  MObs+(1.962*OJI_Mboot$rnd.se)


OJI_Mboot<- cbind(OJI_Mboot, ci1, ci2)
colnames(OJI_Mboot)<- c("MObs", "meanM.boot", "SE", 
								  "CI_low",
								  "CI_high")
#
# Output parameters
# meandf         # Bootstrap mean of parameter values
# SE             # Bootstrap SE for parameter values
# CI_low         # Bootstrap CI (lower) 
# CI_high        # Bootstrap CI (higher) 
OJI_Mboot

```

```{r MAR MODULARITY CI}
M_MAR <- computeModules(intMAR, method="Beckett", deep= FALSE, 
					   deleteOriginalFiles= FALSE, steps= 1000, 
					   tolerance= 1e-10, experimental= FALSE, forceLPA= FALSE)
intMAR<-as.data.frame(intMAR)
M_MAR@likelihood

MObs<- M_MAR@likelihood

MAR_Mboot <- as.data.frame(cbind(MObs, # colMeans(m.boot)))
									 colMeans(m.boot<-m_boot(intMAR, 99))))
rnd.se <- apply(m.boot,2,sd)/sqrt(length(m.boot))   # SE randomized parameters
MAR_Mboot<- cbind(MAR_Mboot, rnd.se)
ci1 <-  MObs-(1.962*MAR_Mboot$rnd.se)
ci2 <-  MObs+(1.962*MAR_Mboot$rnd.se)


MAR_Mboot<- cbind(MAR_Mboot, ci1, ci2)
colnames(MAR_Mboot)<- c("MObs", "meanM.boot", "SE", 
								  "CI_low",
								  "CI_high")
#
# Output parameters
# meandf         # Bootstrap mean of parameter values
# SE             # Bootstrap SE for parameter values
# CI_low         # Bootstrap CI (lower) 
# CI_high        # Bootstrap CI (higher) 
MAR_Mboot
```

#Hamming Distances:
```{r Hamming distances}
library(network)
library(sna)

dim(intMAR)
dim(intOJI)
dim(intCOL)


rowSums(intMAR)
rowSums(intOJI)
rowSums(intCOL)

wMAR <- intMAR     # dim 35x7  
wOJI <- intOJI     # dim 35x7 
wCOL <- intCOL     # dim 35x7

wMAR<- as.data.frame(intMAR)
wOJI<- as.data.frame(intOJI)
wCOL<- as.data.frame(intCOL)

#I delete plants without interactions

wMAR<- wMAR %>%  dplyr::filter(rowSums(wMAR^2)!=0) 
dim(wMAR)    # 34x7

wOJI<- wOJI %>%  dplyr::filter(rowSums(wOJI^2)!=0) 
dim(wOJI)    # 35x7                                 ¡¡ UNA PLANTA MÁS !!

wCOL<- wCOL %>%  dplyr::filter(rowSums(wCOL^2)!=0) 
dim(wCOL)    # 34x7

# I transform the matrices to the same size = 34x7
set.seed(99) 
rOJI<- sample_n(wOJI, 34, replace= F)   # I randomly select 34 plants (without replacement) in OJI, to eliminate one.
dim(wMAR)
dim(rOJI)
dim(wCOL) 

# I generate the graph object
net.wMAR<- graph_from_incidence_matrix(wMAR, weighted= T, add.names=NULL)
net.rOJI<- graph_from_incidence_matrix(rOJI, weighted= T, add.names=NULL) 
net.wCOL<- graph_from_incidence_matrix(wCOL, weighted= T, add.names=NULL) 

mat.wMAR <- get.adjacency(net.wMAR, attr = "weight")
mat.rOJI <- get.adjacency(net.rOJI, attr = "weight")
mat.wCOL <- get.adjacency(net.wCOL, attr = "weight")

grMAR <- network::as.network(as.matrix(mat.wMAR), directed=FALSE, bipartite=22, ignore.eval=FALSE, names.eval='weight')
grOJI <- network::as.network(as.matrix(mat.rOJI), directed=FALSE, bipartite=22, ignore.eval=FALSE, names.eval='weight')
grCOL <- network::as.network(as.matrix(mat.wCOL), directed=FALSE, bipartite=22, ignore.eval=FALSE, names.eval='weight')

# OJI-MAR Comparison

junipA<- base::array(dim=c(2,34,7))
junipA[1,,]<- as.matrix(rOJI)
junipA[2,,]<- as.matrix(wMAR)

q.junipA <- qaptest(junipA,hdist,g1=1,g2=2)
summary(q.junipA)

#OJI-COL Comparison
junipB<- base::array(dim=c(2,34,7))
junipB[1,,]<- as.matrix(rOJI)
junipB[2,,]<- as.matrix(wCOL)

q.junipB <- qaptest(junipB,hdist,g1=1,g2=2)
summary(q.junipB)

# MAR-COL Comparison
junipC<- base::array(dim=c(2,34,7))
junipC[1,,]<- as.matrix(wMAR)
junipC[2,,]<- as.matrix(wCOL)

q.junipC <- qaptest(junipC,hdist,g1=1,g2=2)
summary(q.junipC)

# Creating results table
networkpair<-c("OJI-MAR", "OJI-COL", "MAR-COL")
distance<-c(q.junipA$testval,q.junipB$testval,q.junipC$testval)

hammingdistanceresults<-data.frame(NETWORKS_PAIR = networkpair, Hamming_distance= distance)
kable(hammingdistanceresults)
```

#Plotting network statistics
```{r Species level}
#dataframespecieslevel

dataframestrength<-dataframespecieslevel[22:42,]


dataframestrength$AREA<-recode_factor(dataframestrength$AREA, SABMAR ="ASABMAR",SABOJI = "BSABOJI")
dataframeplantlevel$AREA<-recode_factor(dataframeplantlevel$AREA, SABMAR ="ASABMAR",SABOJI = "BSABOJI")
#levels(dataframestrength$AREA)
#levels(dataframeplantlevel$AREA)

dataframespecieslevel$AREA<-as.factor(dataframespecieslevel$AREA)
dataframespecieslevel$Metric<-as.factor(dataframespecieslevel$Metric)
dataframespecieslevel$Species<-as.factor(dataframespecieslevel$Species)
dataframespecieslevel$Value<-as.numeric(dataframespecieslevel$Value)


dataframeplantlevel$AREA<-as.factor(dataframeplantlevel$AREA)
dataframeplantlevel$Metric<-as.factor(dataframeplantlevel$Metric)
dataframeplantlevel$Species<-as.factor(dataframeplantlevel$Species)
dataframeplantlevel$Value<-as.numeric(dataframeplantlevel$Value)


dataframestrength$Species<-recode_factor(dataframestrength$Species, fa_4cone_chl ="1verderon")
dataframestrength$Species<-recode_factor(dataframestrength$Species, fa_mus ="2mus")
dataframestrength$Species<-recode_factor(dataframestrength$Species, fa_apo ="3apo")
dataframestrength$Species<-recode_factor(dataframestrength$Species, fa_apo ="3apo")

PLOT_STRENGTH<-ggplot(data=dataframestrength, aes(x=AREA, y=Value, fill=Species)) +
  geom_bar(stat="identity", position=position_dodge())+ 
theme_minimal()+ scale_fill_manual("legend", values = c( "#00441b", "#74c476" ,"#238b45","#cc4c02" ,"#662506" ,"#ec7014" , "#fee391"))+ ggtitle("SPECIES STRENGTH") + theme(legend.position="top")



PLOT_STRENGTH #I edit some aspect of this plot in illustrator. 


plants_degree<-dataframeplantlevel[1:103,]
plants_strength<-dataframeplantlevel[104:206,]
plants_strength<-plants_strength[order(plants_strength$Value),]

intCOLmetricPLANTS<-intCOLmetricPLANTS[order(intCOLmetricPLANTS$species.strength,decreasing =  TRUE),]
COL_PLANT_STRENGTH<-(intCOLmetricPLANTS$species.strength)
COL_PLANT_names<-c("C075", "C024", "C083", "C150", "C140", "C126" ,"C106","C285" ,"C057" ,"C054", "C065" ,"C176", "C017", "C316" ,"C014", "C172", "C050" ,"C002", "C165", "C131", "C174", "C056", "C141" ,"C121" ,"C168", "C086" ,"C153", "C162" ,"C193", "C107" ,"C119" ,"C018", "C055" ,"C111")

barplot(COL_PLANT_STRENGTH, names.arg=COL_PLANT_names, las=2, cex.names=0.6,ylim = c(0, 1), xlab = "Individual Plants", ylab = "Node Strength", main = "COL")



intOJImetricPLANTS<-intOJImetricPLANTS[order(intOJImetricPLANTS$species.strength,decreasing =  TRUE),]
OJI_PLANT_STRENGTH<-(intOJImetricPLANTS$species.strength)
OJI_PLANT_names<-c("O580", "O304", "O067" ,"O042", "O766" ,"O334", "O148", "O514", "O072" ,"O682", "O137" ,"O054", "O123", "O642", "O112", "O685", "O023" ,"O314" ,"O231", "O582", "O105" ,"O008" ,"O045" ,"O352", "O621" ,"O384", "O006" ,"O268", "O839" ,"O626", "O553", "O463", "O136", "O241", "O488")

barplot(OJI_PLANT_STRENGTH, names.arg=OJI_PLANT_names, las=2, cex.names=0.6,ylim = c(0, 1), xlab = "Individual Plants", ylab = "Node Strength", main = "OJI")

intMARmetricPLANTS<-intMARmetricPLANTS[order(intMARmetricPLANTS$species.strength,decreasing =  TRUE),]


MAR_PLANT_STRENGTH<-(intMARmetricPLANTS$species.strength)
MAR_PLANT_names<-c("M956", "M087", "M849", "M144", "M664", "M581", "M843", "M826", "M694" ,"M749" ,"M136" ,"M215" ,"M381" ,"M460" ,"M058" ,"M986" ,"M315", "M541", "M520" ,"M029" ,"M531" ,"M036", "M648", "M304", "M457", "M207" ,"M820", "M702", "M847", "M208", "M176", "M065" ,"M219", "M518")
barplot(MAR_PLANT_STRENGTH, names.arg=MAR_PLANT_names, las=2, cex.names=0.6,ylim = c(0, 1), xlab = "Individual Plants", ylab = "Node Strength", main = "MAR")
```
# I bring the results of network level metrics to gather all the plots into one which will be: Figure 4
```{r NETWORK-LEVEL METRICS DATAFRAME INMPUT}
library(readr)

tabletoplot <- read_delim ("~/Documents/GitHub/JEcology_Isla2022/data/tableSMS4toplot.csv", ";", escape_double = FALSE, col_types = cols(WC = col_number(), 
        WC_min = col_number(), WC_max = col_number(), 
        WNODF = col_number(), WNODF_min = col_number(), 
        WNODF_max = col_number(), M = col_number(), 
        M_min = col_number(), M_max = col_number(), 
        H2 = col_number(), H2_min = col_number(), 
        H2_MAX = col_number()),trim_ws = TRUE)


tabletoplot<-as.data.frame(tabletoplot)
tabletoplot$area<-as.factor(tabletoplot$area)

levels (tabletoplot$area)

tabletoplot <- tabletoplot %>% mutate(area = factor(area, levels = c( "SABMAR", "SABOJI","SABCOL")))

tabletoplot$area = factor(tabletoplot$area, levels=c("SABMAR", "SABOJI", "SABCOL"))


levels(tabletoplot$area)

sabcolors <- c("SABCOL"="#35978f", "SABOJI"="#dfc27d", "SABMAR"="#8c510a")

p1<-ggplot(tabletoplot, aes(x=factor(area), y=WC, color= area)) + 
    geom_point(size=3) +
    geom_errorbar(aes(ymin =WC_min, ymax=WC_max), width = 0.3, size = 0.75) + 
    theme_classic() +
    labs(x = "area",y = "WC") +
    scale_color_manual(values=sabcolors) +
    theme(axis.title.x = element_blank(), axis.text.x = element_blank(),legend.position = "none")


p2<-ggplot(tabletoplot, aes(x=factor(area), y=WNODF, color= area)) + 
    geom_point(size=3) +
    geom_errorbar(aes(ymin =WNODF_min, ymax=WNODF_max), width = 0.3, size = 0.75) + 
    theme_classic() +
    labs(x = "area",y = "WNODF") +
    scale_color_manual(values=sabcolors) +
    theme(axis.title.x = element_blank(), axis.text.x = element_blank(), legend.position = "none")


p3<-ggplot(tabletoplot, aes(x=factor(area), y=M, color= area)) + 
    geom_point(size=3) +
    geom_errorbar(aes(ymin =M_min, ymax=M_max), width = 0.3, size = 0.75) + 
    theme_classic() +
    labs(x = "area",y = "M") +
    scale_color_manual(values=sabcolors)  +
    theme(legend.position = "none")


p4<-ggplot(tabletoplot, aes(x=factor(area), y=H2, color= area)) + 
    geom_point(size=3) +
    geom_errorbar(aes(ymin =H2_min, ymax=H2_MAX), width = 0.3, size = 0.75) + 
    theme_classic() +
    labs(x = "area",y = "H2") +
    scale_color_manual(values=sabcolors)  +
    theme(legend.position = "none")


library(patchwork)

PLOT_STRENGTH/(p1+ p2 +p3 )
```

INTERACTION STRENGTH AND PREVALENCE PLOT
```{r INTERACTION STRENGTH AND PREVALENCE PLOT}
Prev_Ant <- read_delim ("~/Documents/GitHub/JEcology_Isla2022/data/Prev_Ant.csv", ",", escape_double = FALSE, trim_ws = TRUE)

p_jorge_Mar<-effectiveness_plot(q1=Prev_Ant$M_prev,q2=Prev_Ant$M_int, 
                                    q2.error =Prev_Ant$SE_M,pts.color= Prev_Ant$Species,pts.size=4, nlines=12,
                                    myxlab= "Prevalence (%)",
                                    myylab="Intensity (%)")+xlim(0,115)+ ggtitle("MAR")

p_jorge_Oji<-effectiveness_plot(q1=Prev_Ant$O_prev,q2=Prev_Ant$O_int, 
                                q2.error =Prev_Ant$SE_O,pts.color= Prev_Ant$Species,pts.size=4, nlines=12,
                                myxlab= "Prevalence (%)",
                                myylab="Intensity (%)")+xlim(0,115)+ggtitle("OJI")

p_jorge_Col<-effectiveness_plot(q1=Prev_Ant$C_prev,q2=Prev_Ant$C_int, 
                                q2.error =Prev_Ant$SE_C,pts.color= Prev_Ant$Species,pts.size=4, nlines=12,
                                myxlab= "Prevalence (%)",
                                myylab="Intensity (%)")+xlim(0,115)+ggtitle("COL")
```

