---
title: "VIF"
author: "Jorge"
date: "3/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
We tested for multicollinearity (VIF factors) among predictor variables, setting a conservative threshold of 3 (package ‘vif’ in R) and excluding redundant variables"

```{r Loading packages}
library(VIF)
library(fmsb)
library(readr)
library(corrplot)
library(tidyr)
library(ggplot2)
library(dplyr)
library(tibble)
```

```{r Data loading}
data <- read_delim ("~/Documents/GitHub/JEcology_Isla2022/data/dataset.csv", ";", escape_double = FALSE, trim_ws = TRUE)

data<-column_to_rownames(data, var = "tree")%>% 
  mutate(area = factor(area, levels = c("SABCOL", "SABOJI", "SABMAR"))) # tree identification to row names.


data$d1 <- as.numeric(data$d1)
data$d2 <- as.numeric(data$d2)
data$h <- as.numeric(data$h)
data$cover <- as.numeric(data$cover)
data$collapsed_cropsize <- as.numeric(data$collapsed_cropsize)
data$neighboiurhood_cropsize <- as.numeric(data$neighboiurhood_cropsize)

data$long <- as.numeric(data$long)
data$diam <- as.numeric(data$diam)
data$cowe <- as.numeric(data$cowe)
data$nseed <- as.numeric(data$nseed)
data$totalseedw <- as.numeric(data$totalseedw)
data$oneseedw <- as.numeric(data$oneseedw)
data$fweight <- as.numeric(data$fweight)
data$sunken <- as.numeric(data$sunken)

data$neighboiurhood_cropsize <- as.numeric(data$neighboiurhood_cropsize)
data$n_neigh <- as.numeric(data$n_neigh)

dataVIF<-data[,-c(1,17,18,19,20,21,22,23,24,25)] # Removed =  AREA,,INTERACTION DATA and x and y coordenates for VIF analyses.
```

#Correlation plot
```{r Raw correlations PLOT}
#data.cor = cor(dataVIF)
#corrplot(data.cor)
```

#Evaluating multicolinearity
```{r}
require(VIF)

vif_func <- function(in_frame,thresh=10,trace=T,...){
  
  require(fmsb)
  
  if(class(in_frame) != 'data.frame') in_frame <- data.frame(in_frame)
  
  #get initial vif value for all comparisons of variables
  vif_init<-NULL
  for(val in names(in_frame)){
    form_in<-formula(paste(val,' ~ .'))
    vif_init<-rbind(vif_init,c(val,VIF(lm(form_in,data=in_frame,...))))
  }
    vif_max<-max(as.numeric(vif_init[,2]))
  
  if(vif_max < thresh){
    if(trace==T){ #print output of each iteration
      prmatrix(vif_init,collab=c('var','vif'),rowlab=rep('',nrow(vif_init)),quote=F)
      cat('\n')
      cat(paste('All variables have VIF < ', thresh,', max VIF ',round(vif_max,2), sep=''),'\n\n')
    }
    return(names(in_frame))
  }
  else{
    
    in_dat<-in_frame
    
    #backwards selection of explanatory variables, stops when all VIF values are below 'thresh'
    while(vif_max >= thresh){
      
      vif_vals<-NULL
      
      for(val in names(in_dat)){
        form_in<-formula(paste(val,' ~ .'))
        vif_add<-VIF(lm(form_in,data=in_dat,...))
        vif_vals<-rbind(vif_vals,c(val,vif_add))
      }
      max_row<-which(vif_vals[,2] == max(as.numeric(vif_vals[,2])))[1]
      
      vif_max<-as.numeric(vif_vals[max_row,2])
      
      if(vif_max<thresh) break
      
      if(trace==T){ #print output of each iteration
        prmatrix(vif_vals,collab=c('var','vif'),rowlab=rep('',nrow(vif_vals)),quote=F)
        cat('\n')
        cat('removed: ',vif_vals[max_row,1],vif_max,'\n\n')
        flush.console()
      }
      
      in_dat<-in_dat[,!names(in_dat) %in% vif_vals[max_row,1]]
      
    }
    
    return(names(in_dat))
    
  }
  
}

dataVIF<-scale(dataVIF)

vif_func(in_frame= dataVIF, thresh=3, trace=T)
```

#Result and final decision: 
Remaining variables: "d1","h","collapsed_cropsize", "neighboiurhood_cropsize", "n_neigh", ,"diam","nseed","oneseedw","sunken"

*I decided to remove cone length, because its information is also provided by cone diameter.

```{r Definitive correlation plot}
dataVIF<-as.data.frame(dataVIF)
data_resist<-dataVIF[, c(1,3,5,6,7,9,11,13,15)]
data.cor2 = cor(data_resist)
corrplot(data.cor2)
```